\LARGE Performance Evaluation of Xenomai 3

### 2015-10-21 paper.tex
initial conclusion

This paper would be a report on performance measurements between upstream Linux real-time enhancements and Xenomai official stable release (both version 2 and 3 series), and the benchmarks show that the maximum response time to external interrupts of the dual kernel configurations for Xenomai 3 is almost twice as PPREEMPT\_RT, that implies more predictable handling on multiple incoming interrupts where Xenomai 3 supports both configurations interchangeably.
\end{abstract}

@@

In Xenomai 3, with the introduction of the \textit{Copperplate} interface, which mediates between the real-time API / emulator of given application uses, and the underlying real-time core. That is, applications are able to run in either environments without visible code change. We do not intend to measure the overhead of \textit{Copperplate} interface or its implementation for the sake of measuring the system-level performance rather than API-oriented emulation.

@@

\section{Conclusions}

>>>>

This paper would be a report on performance measurements between upstream Linux real-time enhancements and Xenomai official stable release (both version 2 and 3 series), and the benchmarks show that the maximum response time to external interrupts of the dual kernel configurations for Xenomai 3 is still better than PPREEMPT\_RT, that implies more predictable handling on multiple incoming interrupts where Xenomai 3 supports both configurations interchangeably.
\end{abstract}

@@

In Xenomai 3, with the introduction of the \textit{Copperplate} interface, which mediates between the real-time API / emulator of given application uses, and the underlying real-time core. That is, applications are able to run in either environments without visible code change.

The default interfaces have switched to being POSIX-based (Copperplate library) in Xenomai 3, so all other real-time APIs (or skins) are implemented on top of this. In particular, the Xenomai 2 native API (now called Alchemy) is a skin, while the POSIX API has been promoted from a skin to the standard interface. We do not intend to measure the overhead of \textit{Copperplate} interface or its implementation for the sake of measuring the system-level performance rather than API-oriented emulation.

@@

\section{Conclusions}
We have evaluated the performance of two approaches to make Linux being real-time: PREEMPT\_RT and Xenomai, diversely presented in the view of single kernel and dual-kernel configurations on single-core ARM Cortex-A8, along with general conclusions about when each kernel configuration. As for the dual kernel configuration of Xenomai 3, latency is still significantly better, but PREEMPT\_RT shows closer performance at least for Linux kernel 3.14 stable release while it enables to run same application on different platforms and migrate existing POSIX application to Linux systems.

The Linux kernel running under Xenomai 3 can be PREEMPT\_RT as well, which means Linux ROOT gets currently running thread's priority through the native option of Xenomai 3 for maximum API/ABI compatibility in real-time environments. For the tight latency requirements such as real-time networking, Xenomai 3 allows to switch to dual kernel configurations utilizing I-pipe for maximum real-time performance. However, our results show some of the unexpected slowdown of Xenomai 3 comparing to Xenomai 2.
